Dominance Regions for Affine Cluster Algebras

### 2022-06-20 affine_dominance.tex
Some more edits

  For $\lambda\in\ZZ^n$ and $r\in\ZZ_{\ge0}$ with $r=ns+\ell$ for $1\le\ell\le n$, the tropical transformation $\phi_{t_r}(\lambda)$ is given by
  \[E^{t_{r-1}}_{\ell,\varepsilon_{r-1}} \cdots E^{t_1}_{2,\varepsilon_1} E^{t_0}_{1,\varepsilon_0} \lambda\]
  for a sequence of signs $\varepsilon_0,\ldots,\varepsilon_{r-1}$ depending on $\lambda$.
  \begin{lemma}
    If $\lambda\in\ZZ^n$ is imaginary, then every sign $\varepsilon_j$ above is equal to $-$.
    \sayDR{Can we use this as a definition of imaginary $\bfg$-vectors?}
  \end{lemma}
  \begin{proof}
    With $1,\ldots,n$ being sink adapted, this choice gives the most complicated transformation at each step.
    That should mean that $\lambda$ is sufficiently far from the initial chamber and remains there under all mutations.
  \end{proof}

>>>>

  For $\lambda\in\ZZ^n$ and $r\in\ZZ_{\ge0}$ with $r=ns+\ell$ for $1\le\ell\le n$, the tropical transformation $\phi_{t_r}(\lambda)$ is given by
  \[E^{t_{r-1}}_{\ell,\varepsilon_{r-1}} \cdots E^{t_{r-\ell}}_{1,\varepsilon_{r-\ell}} E^{t_{ns-1}}_{n,\varepsilon_{ns-1}} \cdots E^{t_1}_{2,\varepsilon_1} E^{t_0}_{1,\varepsilon_0} \lambda\]
  for a sequence of signs $\varepsilon_0,\ldots,\varepsilon_{r-1}$ depending on $\lambda$.
  \begin{lemma}
    If $\lambda\in\ZZ^n$ is imaginary, then every sign $\varepsilon_j$ above is equal to $-$.
    \sayDR{Can we use this as a definition of imaginary $\bfg$-vectors?}
  \end{lemma}
  \begin{proof}
    With $1,\ldots,n$ being sink adapted, this choice gives the most complicated transformation at each step.
    That should mean that $\lambda$ is sufficiently far from the initial chamber and remains there under all mutations.
  \end{proof}

  This would imply that the $\bfc$-vector part of every $E^{t_j}_{k,\varepsilon_j}$ vanishes by Lemma~\ref{lem:tropical signs}, can this be right?
